Driver coverage

### 2024-02-05 scomatic/reports/driver_coverage.Rmd
fix knitting location

knitr::opts_knit$set(root.dir = './')
knitr::opts_chunk$set(
  warning = FALSE, 
  dpi = 300, 
  message = FALSE,
  cache.path = params$cache_dir)

@@

for (info in names(p)) {
  chunks <- c(chunks, paste0('\n####', info))
  message(info)

>>>>

#knitr::opts_knit$set(root.dir = '../')
knitr::opts_chunk$set(
  warning = FALSE, 
  dpi = 300, 
  message = FALSE,
  cache.path = params$cache_dir)

@@

for (info in names(p)) {
  chunks <- c(chunks, paste0('\n#### ', info))
  message(info)
